% Screen - VT100/ANSI Terminal Emulator Cheat Sheet
%
% by Peteris Krumins (peter@catonmat.net)
% http://www.catonmat.net  -  good coders code, great reuse
%
% 2007.09.21
%

\documentclass{article}

\usepackage[left=1.5cm,top=1.5cm,right=1.5cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{menukeys}

\usepackage[pdftex]{hyperref}
\hypersetup{pdftitle={Screen VT100/ANSI Terminal Emulator Cheat Sheet}}
\hypersetup{pdfauthor={Peteris Krumins (peter@catonmat.net)}}
\hypersetup{pdfkeywords={cheat sheet, cheat sheat, cheet sheet, cheet sheat, screen, ansi, vt100, terminal, emulator, unix, linux}}
\hypersetup{pdfsubject={http://www.catonmat.net - good coders code, great reuse}}
%\hypersetup{colorlinks}

\pagestyle{fancy}
\fancypagestyle{plain}{}
\pagenumbering{gobble}

\title{Screen VT100/ANSI Terminal Emulator Cheat Sheet\\
	Default Keyboard Shortcuts}
\author{}
\date{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\renewcommand{\arraystretch}{1.3}


% -----------------------------------------------------------------------

\begin{document}
	\maketitle
	
	\fancyfoot[L]{
		\framebox{\parbox{3.5in}{
		\copyright\ 2007 \textbf{Peteris Krumins} (peter@catonmat.net)\\
		\href{http://www.catonmat.net}{http://www.catonmat.net} - good coders code, great reuse}}
	}

	
	\begin{longtable}[c]{|p{3.5cm}|p{3cm}|p{10cm}|}
		\hline
		\large\textbf{Shortcut} & \large\textbf{Command} & \large\textbf{Description} \\
		\hline
		\endhead
		
		\keys{\ctrl+a} \keys{'} & select & Prompt for a window name or number to switch to. \\
		\hline
		\keys{\ctrl+a} \keys{"} & windowlist -b & Present a list of all windows for selection. \\
		\hline
		\keys{\ctrl+a} \keys{0}\ldots \keys{9} & select 0\ldots select 9 & Switch to window number 0\ldots 9. \\
		\hline
		\keys{\ctrl+a} \keys{-} & select - & Switch to the blank window. \\
		\hline
		\keys{\ctrl+a} \keys{\tab} & focus & Switch the input focus to the next region. \\
		\hline
		\keys{\ctrl+a} \keys{\ctrl+a} & other & Toggle  to  the  window  displayed previously. \\
		\hline
		\keys{\ctrl+a} \keys{a} & meta & Send the command character \keys{\ctrl+a} to window. \\
		\hline
		\keys{\ctrl+a} \keys{A} & title & Allow the user to enter a name for the current window. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{b} \\
			\keys{\ctrl+a} \keys{\ctrl+b}
		\end{tabular}
		& break & Send a break to window. \\
		\hline
		\keys{\ctrl+a} \keys{ B} & pow\_break & Reopen the terminal line and send a break. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{\ctrl+c} \\
			\keys{\ctrl+a} \keys{c}
		\end{tabular}
		& screen & Create a new window with a shell and switch to that window. \\
		\hline
		\keys{\ctrl+a} \keys{C} & clear & Clear the screen. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{d} \\
			\keys{\ctrl+a} \keys{\ctrl+d}
		\end{tabular}
		& detach & Detach screen from this terminal. \\
		\hline
		\keys{\ctrl+a} \keys{D}\keys{D} & pow\_detach & Detach and logout. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{f} \\
			\keys{\ctrl+a} \keys{\ctrl+f}
		\end{tabular}
		& flow & Toggle flow on, off or auto. \\
		\hline
		\keys{\ctrl+a} \keys{F} & fit & Resize the window to the current region size. \\
		\hline
		\keys{\ctrl+a} \keys{\ctrl+g} & vbell & Toggles screen's visual bell mode. \\
		\hline
		\keys{\ctrl+a} \keys{h} & hardcopy & Write a hardcopy of the current window to the file ``hardcopy.n''. \\
		\hline
		\keys{\ctrl+a} \keys{H} & log & Begins/ends logging of the current window to the file ``screenlog.n''. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{i} \\
			\keys{\ctrl+a} \keys{\ctrl+i}
		\end{tabular}
		& info & Show info about this window. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{k} \\
			\keys{\ctrl+a} \keys{\ctrl+k}
		\end{tabular}
		& kill & Destroy current window. \\
		\hline
		\begin{tabular}{@{}l@{}}
		\keys{\ctrl+a} \keys{l} \\
		\keys{\ctrl+a} \keys{\ctrl+l}
		\end{tabular}
		& redisplay & Fully refresh current window. \\
		\hline
		\keys{\ctrl+a} \keys{L} & login & Toggle this windows login slot. Available only if screen is configured to update the utmp database. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{m} \\
			\keys{\ctrl+a} \keys{\ctrl+m}
		\end{tabular}
		& lastmsg & Repeat the last message displayed in the message line. \\
		\hline
		\keys{\ctrl+a} \keys{M} & monitor & Toggles monitoring of the current window. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{\space} \\
			\keys{\ctrl+a} \keys{n} \\
			\keys{\ctrl+a} \keys{\ctrl+n}
		\end{tabular}
		& next & Switch to the next window. \\
		\hline
		\keys{\ctrl+a} \keys{N} & number & Show the number (and title) of the current window. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{\backspace} \\
			\keys{\ctrl+a} \keys{h} \\
			\keys{\ctrl+a} \keys{p} \\
			\keys{\ctrl+a} \keys{\ctrl+p}
		\end{tabular}
		& prev & Switch to the previous window (opposite of \keys{\ctrl+a} \keys{ n}). \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{q} \\
			\keys{\ctrl+a} \keys{\ctrl+q}
		\end{tabular}
		& xon & Send a \keys{\ctrl+q} to the current window. \\
		\hline
		\keys{\ctrl+a} \keys{Q} & only & Delete all regions but the current one. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{r} \\
			\keys{\ctrl+a} \keys{\ctrl+r}
		\end{tabular}
		& wrap & Toggle the current window's line-wrap setting (turn the  current  window's automatic margins on and off). \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{s} \\
			\keys{\ctrl+a} \keys{\ctrl+s}
		\end{tabular}
		& xoff & Send a \keys{\ctrl+s} to the current window. \\
		\hline
		\keys{\ctrl+a} \keys{S} & split & Split the current region into two new ones. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{t} \\
			\keys{\ctrl+a} \keys{\ctrl+t}
		\end{tabular}
		& time & Show system information. \\
		\hline
		\keys{\ctrl+a} \keys{v} & version & Display the version and compilation date. \\
		\hline
		\keys{\ctrl+a} \keys{\ctrl+v} & digraph & Enter digraph. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{w} \\
			\keys{\ctrl+a} \keys{\ctrl+w}
		\end{tabular}
		& windows & Show a list of window. \\
		\hline
		\keys{\ctrl+a} \keys{W} & width & Toggle 80/132 columns. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{x} \\
			\keys{\ctrl+a} \keys{\ctrl+x}
		\end{tabular}
		& lockscreen & Lock this terminal. \\
		\hline
		\keys{\ctrl+a} \keys{X} & remove & Kill the current region. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{z} \\
			\keys{\ctrl+a} \keys{\ctrl+z}
		\end{tabular}
		& suspend & Suspend screen. Your system must support BSD-style job-control. \\
		\hline
		\keys{\ctrl+a} \keys{Z} & reset & Reset the virtual terminal to its ``power-on'' values. \\
		\hline
		\keys{\ctrl+a} \keys{.} & dumptermcap & Write out a ``.termcap'' file. \\
		\hline
		\keys{\ctrl+a} \keys{?} & help & Show key bindings. \\
		\hline
		\keys{\ctrl+a} \keys{\ctrl+\textbackslash} & quit & Kill all windows and terminate screen. \\
		\hline
		\keys{\ctrl+a} \keys{ :} & colon & Enter command line mode. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{[} \\
			\keys{\ctrl+a} \keys{\ctrl+[} \\
			\keys{\ctrl+a} \keys{\esc}
		\end{tabular}
		& copy & Enter copy/scrollback mode. \\
		\hline
		\keys{\ctrl+a} \keys{]} & paste & Write  the contents of the paste buffer to the stdin queue of the current window. \\
		\hline
		\begin{tabular}{@{}l@{}}
			\keys{\ctrl+a} \keys{\{} \\
			\keys{\ctrl+a} \keys{\}}
		\end{tabular}
		& history & Copy and paste a previous (command) line. \\
		\hline
		\keys{\ctrl+a} \keys{\textgreater} & writebuf & Write paste buffer to a file. \\
		\hline
		\keys{\ctrl+a} \keys{\textless} & readbuf & Reads the screen-exchange file into the paste buffer. \\
		\hline
		\keys{\ctrl+a} \keys{=} & removebuf & Removes the file used by \keys{\ctrl+a} \keys{ \textless} and \keys{\ctrl+a} \keys{ \textgreater}. \\
		\hline
		\keys{\ctrl+a} \keys{,} & license & Shows where screen comes from, where it went to and why  you  can  use it. \\
		\hline
		\keys{\ctrl+a} \keys{\_} & silence & Start/stop monitoring the current window for inactivity. \\
		\hline
		\keys{\ctrl+a} \keys{*} & displays & Show a listing of all currently attached displays. \\
		\hline
	\end{longtable}
\end{document}

